---
title: "Untitled"
author: "RN7"
date: "August 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 



- heatwave plots: inspire from uribo's animation gifs   JMA Stats pkg
- japan times article reference
- rise of japanese men using parasols, ignore stigma < health is more important!
- fill map
- joyplot
- thermometer with highest temperature of the day/week/month?
- japan west flooding + heavy rain
- cartogram: non-contiguous, dorling (circles sizes)
- animaton (sf_transitions) >>> japan map morph: hexagonal, cartogram, normal, square, etc.
- yanet garcia
- india kerala flooding
- water basin >>> japan???

prefecture flag map >>> download img use world cup shiny webscrape method


```{r encoding JP script}
source("scripts/source_encoding_932.r")
```



```{r packages, warning=FALSE, message=FALSE}
library(magrittr)
library(jpndistrict)
library(sf)
library(ggimage)
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(ggpomological)
library(scales)
library(rvest)
library(stringr)
library(gganimate)
library(polite)
library(cartogram)
```


```{r sf_ja}
sf_ja <- 1:47 %>% 
    map(~jpndistrict::jpn_pref(pref_code = ., district = FALSE)) %>% 
    reduce(rbind) %>% 
    st_simplify(dTolerance = 0.01)
```


# simple implementation with each prefecture and a temperature (by day, hour, week, watever)

```{r create sample data}
set.seed(8)

ja_weather_df <- sf_ja %>% 
  mutate(dayone = rep(sample(x = 24:34, size = 47, replace = TRUE)),
         dayone_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         dayone_max = rep(sample(x = 35:38, size = 47, replace = TRUE)),
         daytwo = rep(sample(x = 24:34, size = 47, replace = TRUE)),
         daytwo_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         daytwo_max = rep(sample(x = 35:38, size = 47, replace = TRUE)),
         daythree = rep(sample(x = 24:38, size = 47, replace = TRUE)),
         daythree_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         daythree_max = rep(sample(x = 35:38, size = 47, replace = TRUE))) %>% glimpse()

ja_weather_df_fin <- ja_weather_df %>% 
  gather(key = "day", value = "temperature", -jis_code, -prefecture, -geometry) %>% 
  separate(day, into = c("day", "type"), remove = TRUE, sep = "_") %>% 
  mutate(type = case_when(
    is.na(type) ~ "avg",
    TRUE ~ type
  ))

```


```{r sample animation}
# facet to check
ja_weather_df_fin %>% 
  filter(type == "avg") %>% 
  ggplot() +
  geom_sf(aes(fill = temperature)) +
  scale_fill_gradientn(colours = jmastats:::jma_pal(
    palette = "relative", .attribute = FALSE)[5:1],
                            labels = c("35~", "30~35", "25~30", "20~25",
                                       "15~20"),
                            breaks = c(35, 30, 25, 20, 15),
                            limits = c(15, 37)) +
  facet_wrap(~day)



# animation
ja_weather_df_fin %>% 
  ggplot() +
  geom_sf(aes(fill = temperature)) +
  scale_fill_gradientn(colours = jmastats:::jma_pal(
    palette = "relative", .attribute = FALSE)[5:1],
                            labels = c("35~", "30~35", "25~30", "20~25",
                                       "15~20"),
                            breaks = c(35, 30, 25, 20, 15),
                            limits = c(15, 37)) +
  #transition_manual(frames = day)
  transition_states(states = day, 
                    transition_length = 3, 
                    state_length = 1.5) +
  ease_aes('sine-in-out') 

```




# lollipop chart (https://gist.github.com/uribo/3df84211cc48b50ec11655e17ea27ee1)

```{r lollipop chart}
ggplot(data = ja_weather_df_fin %>% filter(type != "avg"), 
       aes(forcats::fct_reorder(prefecture, temperature),
           temperature)) +
  geom_line(aes(group = prefecture), size = 1.2, color = "skyblue") +
  geom_point(aes(color = temperature, group = prefecture), size = 2) + 
  facet_wrap(~day) +
  scale_color_gradientn(colours = jmastats:::jma_pal(palette = "relative", 
                                                     .attribute = FALSE)[5:1],
                        labels = c("35~", "30~35", "25~30", "20~25",
                                   "15~20"),
                        breaks = c(35, 30, 25, 20, 15),
                        limits = c(15, 37)) +
  coord_flip() +
  theme_minimal(base_size = 8) +
  guides(color = guide_legend(title = paste("Temperature", "[\u2103]"),
                              reverse = TRUE,
                              title.position = "left",
                              label.position = "bottom",
                              keywidth = 2,
                              nrow = 1)) +
  theme(legend.position = "bottom") +
  scale_x_discrete(expand = c(0,1)) +
  scale_y_continuous(breaks = seq(0, 40, by = 10),
                     minor_breaks = seq(0, 40, by = 5)) +
  # guides(color = FALSE) +
  labs(x = NULL,
       y = NULL,
       title = "2018年7月31日の各気象観測所における気温",
       subtitle = "日最低・最高気温を表示",
       caption = "Source: 気象庁\nhttp://www.data.jma.go.jp/obd/stats/etrn/index.php")
```





# gg joy plot

```{r joyplot}
library(ggridges)
library(jmastats)

ja_weather_df_fin %>% 
  ggplot(aes(x = temperature, y = day, fill = ..x..)) +
  geom_density_ridges_gradient() +
  scale_fill_jma_absolute(type = "temperature") +
  facet_wrap(~type, ncol = 1)

tokyo_weather_df %>% 
  ggplot(aes(x = avg_temp, y = date, fill = ..x..)) +
  geom_density_ridges_gradient(scale = 10) +
  #facet_grid(~ as.factor(year))
  scale_y_discrete(breaks = c("06/01", "07/01", "08/01", "09/01", "09/30"),
                     labels = c("June 1st", "July 1st", "Aug. 1st", 
                                "Sept. 1st", "Sept. 30th")) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_fill_jma_absolute(type = "temperature")



```

# Hex map
- https://github.com/mikkelkrogsholm/hexamapmaker
- https://uribo.hatenablog.com/entry/2017/10/20/100717
- https://uribo.hatenablog.com/entry/2017/11/08/213751


```{r coord data}
library(magrittr)
library(tidyverse)
library(ggthemes)


df.jp.prefs <- tibble::frame_data(
  ~x, ~y, ~id,
  15, 14, "HKD",
  14, 12, "AOM",
  15, 11, "IWT",
  14, 11, "AKT",
  14, 10, "MYG",
  13, 10, "YGT",
  14, 9, "FKS",
  13, 9, "IBR",
  12, 9, "NGT",
  14, 8, "GNM",
  13, 8, "SIT",
  12, 8, "TCG",
  11, 8, "TYM",
  10, 8, "ISK",
  14, 7, "CHB",
  13, 7, "TKY",
  12, 7, "YMN",
  11, 7, "NGN",
  10, 7, "FKI",
  9, 7, "KYT",
  8, 7, "HYO",
  7, 7, "TTR",
  6, 7, "SMN",
  13, 6, "KNG",
  12, 6, "SZO",
  11, 6, "AIC",
  10, 6, "GIF",
  9, 6, "SIG",
  8, 6, "OSK",
  7, 6, "OKY",
  6, 6, "HRS",
  5, 6, "YMG",
  10, 5, "MIE",
  9, 5, "NAR",
  9, 4, "WKY",
  7, 4, "KGW",
  6, 4, "EHM",
  7, 3, "TKS",
  6, 3, "KUC",
  4, 5, "FKO",
  3, 5, "SAG",
  2, 5, "NGS",
  3, 4, "OIT",
  2, 4, "KUM",
  3, 3, "MYZ",
  2, 3, "KGS",
  1, 1, "OKN"
)
```


```{r hexmap}
library(ggplot2)
library(ggthemes)
ggplot(df.jp.prefs, aes(x = x, y = y, group = id)) +
      geom_point() +
      coord_fixed(ratio = 1) +
      theme_map()

library(hexamapmaker)
df.jp.prefs <- fix_shape(df.jp.prefs)
df.jp.prefs.hex <- make_polygons(df.jp.prefs)

(p <- ggplot(df.jp.prefs.hex, aes(x, y, group = id)) +
    geom_polygon(fill = "white", colour = "black", show.legend = FALSE) +
    coord_fixed(ratio = 1) +
    theme_map())

add_hexalabel(zz = df.jp.prefs.hex, p)

```

- use proper japan spatial data set

```{r hex with sf_ja}
jpn_hex <- sf_ja %>% 
    mutate(
    centroid = map(geometry, st_centroid),
    coords = map(centroid, st_coordinates),
    x = map_dbl(coords, 1),
    y = map_dbl(coords, 2)) %>% 
  select(-centroid, - coords, -jis_code, id = prefecture)

jpn_hex_df <- fix_shape(jpn_hex)
jpn_hex_df <- make_polygons(jpn_hex)

(p <- ggplot(jpn_hex_df, aes(x, y, group = id)) +
    geom_polygon(fill = "white", colour = "black", show.legend = FALSE) +
    coord_fixed(ratio = 1) +
    theme_map())

add_hexalabel(zz = jpn_hex_df, p)

```






# geofacet

```{r geofacet}

```




# temperature maps >>> airport weather stations (RIEM package)


- map() across years of summer months
- combine/compare
- calculate humidex like before as well!

```{r riem}
library(riem)
riem_stations_df <- riem_stations(network = "JP__ASOS")


# web scrape Japan airport codes
session <- bow("https://en.wikipedia.org/wiki/List_of_the_busiest_airports_in_Japan")

japan_airports <- scrape(session) %>% 
  html_nodes("table.wikitable:nth-child(8)") %>% 
  .[[1]] %>% 
  html_table()

japan_airports_clean <- japan_airports %>% 
  janitor::clean_names() %>% 
  mutate(city = cityserved %>% iconv(from = "UTF-8", to = "ASCII//TRANSLIT")) %>% 
  select(airport, city, iata_icao) %>% 
  separate(iata_icao, c("IATA", "ICAO"), "\\/") %>% 
  mutate(city = case_when(
    ICAO == "RJAH" ~ "Ibaraki",
    ICAO == "RJOK" ~ "Kochi",
    TRUE ~ city
  )) %>% 
  filter(!ICAO %in% c("RJAA", "RJBB")) %>% 
  glimpse()


# grab weather data from stations
summer_weather <-  
  map_df(japan_airports_clean$ICAO, riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-12")

# write.csv(summer_weather, file = "japan_summer_weather_06012018_08122018.csv")
# summer_weather <- read.csv("japan_summer_weather_06012018_08122018.csv", 
#                            stringsAsFactors = FALSE)

glimpse(summer_weather)

summer_weather %>% 
  group_by(station) %>% 
  summarise(max_temp = max(tmpf),
            min_temp = min(tmpf))

sum_air <- summer_weather %>% 
  left_join(japan_airports_clean, by = c("station" = "ICAO")) %>% glimpse()

sf_ja %>% 
  ggplot() +
  geom_sf() +
  geom_point(data = sum_air, aes(x = lon, y = lat), color = "red")



```



```{r _at() examples}
japan_airports %>% 
  mutate(city = Cityserved %>% iconv(from = "UTF-8", to = "ASCII//TRANSLIT")) %>% 
  janitor::clean_names() %>% 
  mutate_at(.vars = vars(matches("aircraft|passengers")), 
            .funs = funs(str_replace_all(., ",", "") %>% as.numeric())) %>% 
  glimpse()


japan_airports %>% 
  select_at(vars(matches("aircraft|passengers")))
```




# tokyo weather stations map:

```{r tokyo weather stations}
# just tokyo
sf_pref13 <- jpn_pref(pref_code = 13, district = TRUE) %>% 
    st_simplify(dTolerance = 0.0001) %>% 
    mutate(city_code = as.numeric(city_code)) %>% 
    filter(city_code != 13421) %>%  # filter out the Ogasawara Islands (off the coast)
    st_union() %>% 
    as.data.frame() %>% 
    mutate(jis_code = "13", prefecture = "Tokyo") %>% 
    magrittr::set_names(c("geometry", "jis_code", "prefecture")) %>% 
    st_as_sf()


tky_stations <- jmastats::stations %>% 
  filter(area == "東京") %>% 
  filter(station_type %in% c("四"))

tky_stations %>% 
  mutate(
    centroid = map(geometry, st_centroid),
    coords = map(centroid, st_coordinates),
    coord_x = map_dbl(coords, 1),
    coord_y = map_dbl(coords, 2)) %>% 
  select(-centroid, - coords) -> tky_stations

# longitude = sf::st_coordinates(geometry)[, 1],
# latitude = sf::st_coordinates(geometry)[, 2]

library(ggrepel)
library(ggthemes)
library(emojifont)
library(extrafont)
load.fontawesome()
loadfonts()

tky_stations <- tky_stations %>% 
  mutate(label = fontawesome(c("fa-university")))

sf_pref13 %>% 
  ggplot() +
  geom_sf(fill = "white") +
  coord_sf(xlim = c(138.9, 139.95),
           ylim = c(35.47, 35.9)) +
  geom_label(data = tky_stations, 
             aes(x = coord_x, y = coord_y,
                 label = label),
             family = "fontawesome-webfont") +
  geom_label_repel(data = tky_stations,
             aes(x = coord_x, y = coord_y,
                 label = station_name),
             size = 2, nudge_y = -0.025) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank())


# CRS: 3095 projection
sf_pref13 %>% 
  st_transform(crs = 3095) %>% 
  ggplot() +
  geom_sf(fill = "white") +
  coord_sf(datum = st_crs(3095),
           ylim = c(3900000, 4000000),
           xlim = c(310000, 410000)) 


```

- row is ONE year
- col is each day of the summer

->>> transform in MAP form? use Tokyo 23 wards

```{r}
df_target_stations <-
  stations %>%
  # 観測装置の種類が「有線ロボット気象計」(いわゆるアメダス) であるものに制限
  filter(station_type %in% c("四")) %>%
  filter(block_no != "0092") %>%
  group_by(pref_code, area) %>%
  sample_n(1) %>%
  ungroup() %>%
  select(pref_code, area, station_name, block_no)



df_targets <-
  purrr::map2_dfr(
    .x = df_target_stations$block_no %>%
      set_names(),
    .y = df_target_stations$station_name,
    ~ jma_collect(item = "hourly",
                  block_no = .x,
                  year = 2018,
                  month = 7,
                  day = 31) %>% 
      select(date, time, starts_with("temperature")) %>% 
      #jmastats::parse_unit() %>% 
      mutate(station = .y),
    .id = "block_no")
```


# tile map of TOKYO avg. summer temperature (June-Sept) from Toyo Keizai: https://toyokeizai.net/sp/visual/tko/temperature/

```{r tile map tokyo summer}
library(jsonlite)
library(lubridate)

tokyo_his_temp <- jsonlite::read_json("data/temperature.json", simplifyVector = TRUE)

tokyo_weather_df <- tokyo_his_temp %>% 
  set_names(nm = 1876:2018) %>% 
  map(~as.data.frame(.) %>% 
        modify_if(., is.factor, as.character) %>% 
        modify_if(., is.character, as.numeric)) %>% 
  map2_df(., names(.), ~ mutate(., ID = .y)) %>% 
  rename(avg_temp = ".",
         year = ID)

# separate 2018 as data only up to 7/17
tokyo_weather_df_2018 <- tokyo_weather_df %>% 
  filter(year == 2018) %>% 
  mutate(
    date = seq.Date(from = as.Date("2018-06-01"), 
                    by = "day",
                    length = 47),
    date = format(date, "%m/%d")
  ) 
  
# rest of the years, then combine back
tokyo_weather_df <- tokyo_weather_df %>% 
  filter(year != 2018) %>% 
  group_by(year) %>% 
  mutate(
    date = seq.Date(from = as.Date("1876-06-01"), 
                    by = "day",
                    length = 122),
    date = format(date, "%m/%d")
  ) %>% 
  ungroup() %>% 
  full_join(tokyo_weather_df_2018) %>% 
  mutate(year = as.numeric(year))

glimpse(tokyo_weather_df)

```



```{r}
scale_fill_jma_absolute(
    type = "temperature", 
    guide = "colourbar",
    na.value = "grey50")

dichromat_pal("DarkRedtoBlue.12")(12)
dichromat_pal("DarkRedtoBlue.12")(12)[4:12]

cols <- c("#1a9641", "#a6d96a", "#ffffbf", "#fdae61", "#d7191c")

jmastats:::jma_pal(palette = "relative", .attribute = FALSE)[5:1]

```


```{r plot tokyo summer, fig.height=8, fig.width=10}
library(jmastats)
library(extrafont)
library(scales)
# loadfonts()

# colorbrewer2.org: diverging 8-class palette
cols <- rev(c('#d53e4f','#f46d43','#fdae61','#fee08b','#e6f598','#abdda4','#66c2a5','#3288bd'))

labels <- c("10", "12", "14", "16", "18", "20", "22", "24", "26", "28", "30", "32")

breaks <- c(seq(10, 32, by = 2))

y_labs <- seq(1880, 2015, by = 10)

tokyo_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile() +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  scale_y_reverse(limits = c(2017, 1876), expand = c(0, 0),
                  breaks = c(1876, seq(1880, 2015, by = 10), 2017)) +
  scale_x_discrete(breaks = c("06/01", "07/01", "08/01", "09/01", "09/30"),
                     labels = c("June 1st", "July 1st", "Aug. 1st", 
                                "Sept. 1st", "Sept. 30th")) +
  labs(title = "Summers in Tokyo are Getting Longer and Hotter (1876-2017)",
       subtitle = glue::glue("
          One Row = One Year, From June 1st to September 30th
          Average Temperature (Celsius)
          "),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed", size = 12),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(3, "cm"),
        plot.margin=unit(c(1,1,1.5,1.2),"cm"))

ggsave("tokyo_summer_temp_eng.png", plot = last_plot())
```



```{r LOG avg temp}
tokyo_log_weather_df <- tokyo_weather_df %>% 
  mutate(avg_temp = log10(avg_temp))


tokyo_log_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) + 
  geom_tile() + 
  scale_fill_jma_absolute() +
  scale_y_reverse(limits = c(2020, 1875), expand = c(0, 0))
```



```{r tile map JP version, fig.height=8, fig.width=10}
tokyo_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile() +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("平均気温 " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  labs(title = "東京の夏は「暑く・長く」なっている (1876年～2017年)",
       subtitle = "6月1日～9月30日",
       caption = "データ：気象庁") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed", size = 12),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(3, "cm"))

ggsave("tokyo_summer_temp_jp.png", plot = last_plot(), width = 10, height = 8)
```



- caveat: tokyo prefecutreis very wide: from tokyo bay coastline all the way to mountainous Hachioji area
- not noted whether looking at tokyo weather from just the special 23 wards or the prefecture in general?
- figure out how to add dates grouped by year 
- >>> annoying is that 2018 only has 47 days recorded (as not september yet)...
- just filter out 2018 and set that individually??
- use ggiraph for interactivity?

# ggiraph:


```{r ggiraph data prep}
library(glue)

tokyo_weather_df_ggiraph <- tokyo_weather_df %>% 
  mutate(year = as.character(year),
         date = date %>% str_replace_all("/", "-")) %>% 
  unite(full_date, year, date, sep = "-", remove = FALSE) %>% 
  mutate(full_date = as.Date(full_date) %>% 
           format(., format = "%B %d, %Y"),
         ) %>% 
  glimpse()

tokyo_weather_df_ggiraph <- tokyo_weather_df_ggiraph %>% 
  filter(!year == 2018) %>% 
  mutate(tooltip = glue("
                        {full_date}: {avg_temp}{intToUtf8(176)}C"),
         year = as.numeric(year)) %>% glimpse()

tokyo_weather_df_ggiraph <- tokyo_weather_df_ggiraph %>% 
  filter(!year == 2018) %>% 
  mutate(tooltip = paste(full_date, ": ", avg_temp, intToUtf8(176), "C"),
         year = as.numeric(year)) %>% glimpse()

```

```{r ggiraph, fig.height=8, fig.width=10}
library(ggiraph)

tokyo_weather_ggiraph <- tokyo_weather_df_ggiraph %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile_interactive(aes(x = date, y = year, 
                            fill = avg_temp, 
                            tooltip = tokyo_weather_df_ggiraph$tooltip, 
                            data_id = tokyo_weather_df_ggiraph$tooltip)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df_ggiraph$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  labs(title = "Average Temperature in Tokyo during the Summer (1876-2017)",
       subtitle = glue::glue("
          From June 1st to September 30th
          One Row = One Year"),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(1.5, "cm")) +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0))

ggiraph(code = print(tokyo_weather_ggiraph))

```







```{r}

tkw <- tokyo_weather_df_ggiraph %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile_interactive(aes(x = date, y = year, 
                            fill = avg_temp, 
                            tooltip = tokyo_weather_df_ggiraph$tooltip, 
                            data_id = tokyo_weather_df_ggiraph$tooltip)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df_ggiraph$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                nrow = 1)) +
  labs(title = "Average Temperature in Tokyo during the Summer (1872-2017)",
       subtitle = glue::glue("
          From June 1st to September 30th
          One Row = One Year"),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(2, "cm")) +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0))


ggiraph(code = print(tkw), dep_dir = "C:/Users/Ryo Nakagawara/Documents/R_materials/japan_weather_plots/output")

```


## cartograms



```{r}
ja_weather_df_fin %>% 
  filter(day == "dayone", type == "avg") %>% 
  st_transform(crs = "+init=epsg:3395") -> carto_base

pref_pop_hist %>% 
  filter(!prefectures == "Japan") %>% 
  mutate(code = as.numeric(code)) -> pref_pop_hist


pop_df <- ja_weather_df_fin %>% 
  mutate(jis_code = as.numeric(jis_code)) %>% 
  left_join(pref_pop_hist, c("jis_code" = "code")) %>% glimpse()


pop_df_base <- pop_df %>% 
  filter(day == "dayone", type == "avg", year == 2010) %>% 
  st_transform(crs = "+init=epsg:3395")

```



```{r}
library(tmap)


carto_df <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_dorling("temperature", itermax = 500)

tm_shape(ja_weather_df_fin) + 
  tm_borders() +
  tm_shape(carto_df) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

carto_df <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_dorling("population", itermax = 500)

tm_shape(carto_df) +
  tm_polygons("population", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

```


```{r}
#
carto_nca <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_ncont("temperature")

tm_shape(ja_weather_df_fin) + 
  tm_borders() +
  tm_shape(carto_nca) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)


carto_nca <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_ncont("population")

tm_shape(pop_df_base) + 
  tm_borders() +
  tm_shape(carto_nca) +
  tm_polygons("population", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)


```


```{r}
#

cart_cac <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_cont("temperature", itermax = 10)

tm_shape(cart_cac) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

carto_df <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_cont("population")

tm_shape(carto_df) +
  tm_polygons("population", style = "pretty") +
  tm_layout(frame = FALSE)

```



