---
title: "Untitled"
author: "RN7"
date: "August 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualizing the Weather in Japan: A Sweltering Summer Story



- heatwave plots: inspire from uribo's animation gifs   JMA Stats pkg
- japan times article reference
- rise of japanese men using parasols, ignore stigma < health is more important!
- fill map
- joyplot
- thermometer with highest temperature of the day/week/month?
- japan west flooding + heavy rain
- cartogram: non-contiguous, dorling (circles sizes)
- animaton (sf_transitions) >>> japan map morph: hexagonal, cartogram, normal, square, etc.
- yanet garcia
- india kerala flooding
- water basin >>> japan???
- climate warming stripes: http://www.climate-lab-book.ac.uk/2018/warming-stripes/

prefecture flag map >>> download img use world cup shiny webscrape method


```{r encoding JP script}
source("../scripts/source_encoding_932.r")
```



```{r packages, warning=FALSE, message=FALSE}
library(magrittr)
library(jpndistrict)
library(sf)
library(ggimage)
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(ggpomological)
library(scales)
library(rvest)
library(stringr)
library(gganimate)
library(polite)
library(cartogram)
library(forcats)
library(extrafont)
library(lubridate)
loadfonts()
```


```{r sf_ja}
sf_ja <- 1:47 %>% 
    map(~jpndistrict::jpn_pref(pref_code = ., district = FALSE)) %>% 
    reduce(rbind) %>% 
    st_simplify(dTolerance = 0.01)
```


# simple implementation with each prefecture and a temperature (by day, hour, week, watever)

```{r create sample data}
set.seed(8)

ja_weather_df <- sf_ja %>% 
  mutate(dayone = rep(sample(x = 24:34, size = 47, replace = TRUE)),
         dayone_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         dayone_max = rep(sample(x = 35:38, size = 47, replace = TRUE)),
         daytwo = rep(sample(x = 24:34, size = 47, replace = TRUE)),
         daytwo_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         daytwo_max = rep(sample(x = 35:38, size = 47, replace = TRUE)),
         daythree = rep(sample(x = 24:38, size = 47, replace = TRUE)),
         daythree_min = rep(sample(x = 20:24, size = 47, replace = TRUE)),
         daythree_max = rep(sample(x = 35:38, size = 47, replace = TRUE))) %>% glimpse()

ja_weather_df_fin <- ja_weather_df %>% 
  gather(key = "day", value = "temperature", -jis_code, -prefecture, -geometry) %>% 
  separate(day, into = c("day", "type"), remove = TRUE, sep = "_") %>% 
  mutate(type = case_when(
    is.na(type) ~ "avg",
    TRUE ~ type
  ))

```


```{r sample animation}
# facet to check
ja_weather_df_fin %>% 
  filter(type == "avg") %>% 
  ggplot() +
  geom_sf(aes(fill = temperature)) +
  scale_fill_gradientn(colours = jmastats:::jma_pal(
    palette = "relative", .attribute = FALSE)[5:1],
                            labels = c("35~", "30~35", "25~30", "20~25",
                                       "15~20"),
                            breaks = c(35, 30, 25, 20, 15),
                            limits = c(15, 37)) +
  facet_wrap(~day)



# animation
ja_weather_df_fin %>% 
  ggplot() +
  geom_sf(aes(fill = temperature)) +
  scale_fill_gradientn(colours = jmastats:::jma_pal(
    palette = "relative", .attribute = FALSE)[5:1],
                            labels = c("35~", "30~35", "25~30", "20~25",
                                       "15~20"),
                            breaks = c(35, 30, 25, 20, 15),
                            limits = c(15, 37)) +
  #transition_manual(frames = day)
  transition_states(states = day, 
                    transition_length = 3, 
                    state_length = 1.5) +
  ease_aes('sine-in-out') 

```




# lollipop chart (https://gist.github.com/uribo/3df84211cc48b50ec11655e17ea27ee1)

```{r lollipop chart}
ggplot(data = ja_weather_df_fin %>% filter(type != "avg"), 
       aes(forcats::fct_reorder(prefecture, temperature),
           temperature)) +
  geom_line(aes(group = prefecture), size = 1.2, color = "skyblue") +
  geom_point(aes(color = temperature, group = prefecture), size = 2) + 
  facet_wrap(~day) +
  scale_color_gradientn(colours = jmastats:::jma_pal(palette = "relative", 
                                                     .attribute = FALSE)[5:1],
                        labels = c("35~", "30~35", "25~30", "20~25",
                                   "15~20"),
                        breaks = c(35, 30, 25, 20, 15),
                        limits = c(15, 37)) +
  coord_flip() +
  theme_minimal(base_size = 8) +
  guides(color = guide_legend(title = paste("Temperature", "[\u2103]"),
                              reverse = TRUE,
                              title.position = "left",
                              label.position = "bottom",
                              keywidth = 2,
                              nrow = 1)) +
  theme(legend.position = "bottom") +
  scale_x_discrete(expand = c(0,1)) +
  scale_y_continuous(breaks = seq(0, 40, by = 10),
                     minor_breaks = seq(0, 40, by = 5)) +
  # guides(color = FALSE) +
  labs(x = NULL,
       y = NULL,
       title = "2018年7月31日の各気象観測所における気温",
       subtitle = "日最低・最高気温を表示",
       caption = "Source: 気象庁\nhttp://www.data.jma.go.jp/obd/stats/etrn/index.php")
```





# gg joy plot

```{r joyplot}
library(ggridges)
library(jmastats)

ja_weather_df_fin %>% 
  ggplot(aes(x = temperature, y = day, fill = ..x..)) +
  geom_density_ridges_gradient() +
  scale_fill_jma_absolute(type = "temperature") +
  facet_wrap(~type, ncol = 1)

tokyo_weather_df %>% 
  ggplot(aes(x = avg_temp, y = date, fill = ..x..)) +
  geom_density_ridges_gradient(scale = 10) +
  #facet_grid(~ as.factor(year))
  scale_y_discrete(breaks = c("06/01", "07/01", "08/01", "09/01", "09/30"),
                     labels = c("June 1st", "July 1st", "Aug. 1st", 
                                "Sept. 1st", "Sept. 30th")) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_fill_jma_absolute(type = "temperature")



```

# Hex map
- https://github.com/mikkelkrogsholm/hexamapmaker
- https://uribo.hatenablog.com/entry/2017/10/20/100717
- https://uribo.hatenablog.com/entry/2017/11/08/213751


```{r coord data}
library(magrittr)
library(tidyverse)
library(ggthemes)


df.jp.prefs <- tibble::frame_data(
  ~x, ~y, ~id,
  15, 14, "HKD",
  14, 12, "AOM",
  15, 11, "IWT",
  14, 11, "AKT",
  14, 10, "MYG",
  13, 10, "YGT",
  14, 9, "FKS",
  13, 9, "IBR",
  12, 9, "NGT",
  14, 8, "GNM",
  13, 8, "SIT",
  12, 8, "TCG",
  11, 8, "TYM",
  10, 8, "ISK",
  14, 7, "CHB",
  13, 7, "TKY",
  12, 7, "YMN",
  11, 7, "NGN",
  10, 7, "FKI",
  9, 7, "KYT",
  8, 7, "HYO",
  7, 7, "TTR",
  6, 7, "SMN",
  13, 6, "KNG",
  12, 6, "SZO",
  11, 6, "AIC",
  10, 6, "GIF",
  9, 6, "SIG",
  8, 6, "OSK",
  7, 6, "OKY",
  6, 6, "HRS",
  5, 6, "YMG",
  10, 5, "MIE",
  9, 5, "NAR",
  9, 4, "WKY",
  7, 4, "KGW",
  6, 4, "EHM",
  7, 3, "TKS",
  6, 3, "KUC",
  4, 5, "FKO",
  3, 5, "SAG",
  2, 5, "NGS",
  3, 4, "OIT",
  2, 4, "KUM",
  3, 3, "MYZ",
  2, 3, "KGS",
  1, 1, "OKN"
)
```


```{r hexmap}
library(ggplot2)
library(ggthemes)
ggplot(df.jp.prefs, aes(x = x, y = y, group = id)) +
      geom_point() +
      coord_fixed(ratio = 1) +
      theme_map()

library(hexamapmaker)
df.jp.prefs <- fix_shape(df.jp.prefs)
df.jp.prefs.hex <- make_polygons(df.jp.prefs)

(p <- ggplot(df.jp.prefs.hex, aes(x, y, group = id)) +
    geom_polygon(fill = "white", colour = "black", show.legend = FALSE) +
    coord_fixed(ratio = 1) +
    theme_map())

add_hexalabel(zz = df.jp.prefs.hex, p)

```

- use proper japan spatial data set

```{r hex with sf_ja}
jpn_hex <- sf_ja %>% 
    mutate(
    centroid = map(geometry, st_centroid),
    coords = map(centroid, st_coordinates),
    x = map_dbl(coords, 1),
    y = map_dbl(coords, 2)) %>% 
  select(-centroid, - coords, -jis_code, id = prefecture)

jpn_hex_df <- fix_shape(jpn_hex)
jpn_hex_df <- make_polygons(jpn_hex)

(p <- ggplot(jpn_hex_df, aes(x, y, group = id)) +
    geom_polygon(fill = "white", colour = "black", show.legend = FALSE) +
    coord_fixed(ratio = 1) +
    theme_map())

add_hexalabel(zz = jpn_hex_df, p)

```






# geofacet

```{r geofacet}

```




# temperature maps >>> airport weather stations (RIEM package)


- map() across years of summer months
- combine/compare
- calculate humidex like before as well!

```{r riem}
library(riem)
riem_stations_df <- riem_stations(network = "JP__ASOS")


# web scrape Japan airport codes
session <- bow("https://en.wikipedia.org/wiki/List_of_the_busiest_airports_in_Japan")

japan_airports <- scrape(session) %>% 
  html_nodes("table.wikitable:nth-child(8)") %>% 
  .[[1]] %>% 
  html_table()

japan_airports_clean <- japan_airports %>% 
  janitor::clean_names() %>% 
  mutate(city = cityserved %>% iconv(from = "UTF-8", to = "ASCII//TRANSLIT")) %>% 
  select(airport, city, iata_icao) %>% 
  separate(iata_icao, c("IATA", "ICAO"), "\\/") %>% 
  mutate(city = case_when(
    ICAO == "RJAH" ~ "Ibaraki",
    ICAO == "RJOK" ~ "Kochi",
    TRUE ~ city
  )) %>% 
  filter(!ICAO %in% c("RJAA", "RJBB")) %>% 
  glimpse()



safe_riem_measures <- safely(riem_measures)

# grab weather data from stations
summer_weather_raw <-  
  map_df(japan_airports_clean$ICAO, safe_riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-31")


```





not working for some codes apparently... hmmmmmm...

```{r}
japan_airports_clean$ICAO %>% head() -> jac_1

summer_weather <-  
  map_df(jac_1, riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-24")

japan_airports_clean %>% slice(7:17) %>% select(ICAO) %>% as_vector() -> jac_2

summer_weather2 <-  
  map_df(jac_2, riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-24")

japan_airports_clean %>% slice(17:30) %>% select(ICAO) %>% as_vector() -> jac_3

summer_weather3 <-  
  map_df(jac_3, riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-24")

japan_airports_clean %>% slice(33:35) %>% select(ICAO) %>% as_vector() -> jac_4

summer_weather4 <-  
  map_df(jac_4, riem_measures,
         date_start = "2018-06-01",
         date_end = "2018-08-24")


# write.csv(summer_weather, file = "japan_summer_weather_06012018_08122018.csv")
# summer_weather <- read.csv("japan_summer_weather_06012018_08122018.csv", 
#                            stringsAsFactors = FALSE)

glimpse(summer_weather)

summer_weather %>% 
  group_by(station) %>% 
  summarise(max_temp = max(tmpf),
            min_temp = min(tmpf))

sum_air <- summer_weather %>% 
  left_join(japan_airports_clean, by = c("station" = "ICAO")) %>% glimpse()

sum_air %>% 
  mutate(jis_code = case_when(
    city == "Tokyo" ~ 13,
    city == "Fukuoka" ~ 40,
    city == "Sapporo" ~ 1,
    city == "Naha" ~ 47,
    city == "Osaka" ~ 27,
    city == "Nagoya" ~ 23
  )) -> sum_air_codes


# crazily granular >>> 30 minute intervals! TMI 
sum_air_pref <- sum_air_codes %>% 
  left_join(sf_ja %>% mutate(jis_code = as.numeric(jis_code)), by = "jis_code") %>% 
  mutate(time = as_date(valid) %>% ymd()) %>% 
  separate(time, into = c("year", "month", "day"), sep = "-") %>% 
  group_by(month, day, station) %>% 
  summarize(max_temp = max(tmpf),
            min_temp = min(tmpf))

```


```{r skimr + kable}
sum_air %>% 
  skimr::skim_to_wide() %>% 
  knitr::kable()
```



```{r}
sum_air_pref %>% 
  ggplot(aes(x = valid, y = tmpf))

```


```{r}

sf_ja %>% 
  ggplot() +
  geom_sf() +
  geom_point(data = sum_air, aes(x = lon, y = lat), color = "red")

```



```{r _at() examples}
japan_airports %>% 
  mutate(city = Cityserved %>% iconv(from = "UTF-8", to = "ASCII//TRANSLIT")) %>% 
  janitor::clean_names() %>% 
  mutate_at(.vars = vars(matches("aircraft|passengers")), 
            .funs = funs(str_replace_all(., ",", "") %>% as.numeric())) %>% 
  glimpse()


japan_airports %>% 
  select_at(vars(matches("aircraft|passengers")))
```



# jma stats 

```{r jmastats data}
library(jmastats)
jpnprefs <- jpndistrict::jpnprefs

tky <- jpnprefs %>% filter(jis_code == 13)

lat <- jpnprefs %>% select(capital_latitude) %>% as_vector()
lon <- jpnprefs %>% select(capital_longitude) %>% as_vector()

tokyo_station <- nearest_station(latitude = tky$capital_latitude, 
                                 longitude = tky$capital_longitude)

tky_station2 <- pick_neighbor_stations(latitude = tky$capital_latitude,
                                       longitude = tky$capital_longitude,
                                       distance = 10, .unit = "km")

stuf <- list(x = lon, y = lat)

map2(x = lon, y = lat, 
        .f = nearest_station(longitude = .x, latitude = .y)) -> jpn_coord_stations

japan_one_stations <- map2(lon, lat, ~ nearest_station(.x, .y, geometry = NULL))

saveRDS(japan_one_stations, file = "../data/japan_stations_coords.RDS")


j_stat_ref <- japan_one_stations %>% 
  map(~as.data.frame(.)) %>% 
  reduce(rbind) 
```

```{r}
# interestingly, the nearest_stations() function gives us a column showing how far away the station
# is from the coordinates we supplied it with
# let's take a look!

j_stat_ref %>% 
  summarize(avg_distance = mean(distance) / 1000)

# so on avg. the stations were  2.2 km away from the prefecture capital coordinates we gave the fun
# that's good enough for me!

```


```{r}
j_station_df <- j_stat_ref %>% 
  select(-geometry) %>% 
  left_join(stations %>% st_set_geometry(NULL), by = c("station_no", "area", "station_name")) %>% 
  glimpse()


# erase duplicates

j_ws_df <- j_station_df %>% 
  distinct(station_name, .keep_all = TRUE) %>% 
  glimpse()

# now we got one station per prefecture that is as close to the capital as possible!

```


```{r warning=FALSE, message=FALSE}
month <- c(6, 7, 8, 9)
block_no <- j_ws_df %>% select(block_no) %>% as_vector()


df <- crossing(block_no, month)

j_sum_weather_raw <- map2(.x = df$block_no, .y = df$month, 
        ~ jma_collect(item = "daily", block_no = .x, year = 2018, month = .y) %>% 
          mutate(block = .x))

saveRDS(j_sum_weather_raw, file = "../data/j_all_weather_raw.RDS")

df <- df %>% 
  unite("name", c("block_no", "month"), remove = FALSE) %>% 
  glimpse()

j_sum_weather_df <- j_sum_weather_raw %>% 
  bind_rows() %>% 
  glimpse()

saveRDS(j_sum_weather_df, file = "../data/j_all_weather_df.RDS")
```

## sanity check jmastats

OK, let's just make a quick check to make sure the temperature we got for each months/station pair is the correct one. Always check your work!

```{r check right list order}
sumo_montho <- map(.x = list(6, 7, 8), ~jma_collect(item = "daily", block_no = "0363", 
                            year = 2018, month = .x))

sumo_month_df <- sumo_montho %>% 
  set_names(c("june", "july", "aug")) %>% 
  bind_rows(., .id = "monthos") %>% 
  select(monthos, date, avg_temp = `temperature_average(℃)`) %>% 
  glimpse()

sumo_month_df %>% 
  mutate(station = "0363") %>% 
  left_join(jj, by = c("station" = "block", "date")) %>% 
  select(date, avg_temp, `temperature_average(℃)`, station) %>% 
  head(10)

```

Right so avg_temp is from the one the data we just created that is definitely from station 0363 and the temperature_average is from the large dataframe we crossed + map'd earlier. Looking at `head(10)` and `tail(10)` (not shown here) the data matches up properly. (phew...)


# tokyo weather stations map:

```{r tokyo weather stations}
# just tokyo
sf_pref13 <- jpn_pref(pref_code = 13, district = TRUE) %>% 
    st_simplify(dTolerance = 0.0001) %>% 
    mutate(city_code = as.numeric(city_code)) %>% 
    filter(city_code != 13421) %>%  # filter out the Ogasawara Islands (off the coast)
    st_union() %>% 
    as.data.frame() %>% 
    mutate(jis_code = "13", prefecture = "Tokyo") %>% 
    magrittr::set_names(c("geometry", "jis_code", "prefecture")) %>% 
    st_as_sf()


tky_stations <- jmastats::stations %>% 
  filter(area == "東京") %>% 
  filter(station_type %in% c("四"))

tky_stations %>% 
  mutate(
    centroid = map(geometry, st_centroid),
    coords = map(centroid, st_coordinates),
    coord_x = map_dbl(coords, 1),
    coord_y = map_dbl(coords, 2)) %>% 
  select(-centroid, - coords) -> tky_stations

# longitude = sf::st_coordinates(geometry)[, 1],
# latitude = sf::st_coordinates(geometry)[, 2]

library(ggrepel)
library(ggthemes)
library(emojifont)
library(extrafont)
load.fontawesome()
loadfonts()

tky_stations <- tky_stations %>% 
  mutate(label = fontawesome(c("fa-university")))

sf_pref13 %>% 
  ggplot() +
  geom_sf(fill = "white") +
  coord_sf(xlim = c(138.9, 139.95),
           ylim = c(35.47, 35.9)) +
  geom_label(data = tky_stations, 
             aes(x = coord_x, y = coord_y,
                 label = label),
             family = "fontawesome-webfont") +
  geom_label_repel(data = tky_stations,
             aes(x = coord_x, y = coord_y,
                 label = station_name),
             size = 2, nudge_y = -0.025) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank())


# CRS: 3095 projection
sf_pref13 %>% 
  st_transform(crs = 3095) %>% 
  ggplot() +
  geom_sf(fill = "white") +
  coord_sf(datum = st_crs(3095),
           ylim = c(3900000, 4000000),
           xlim = c(310000, 410000)) 


```

- row is ONE year
- col is each day of the summer

->>> transform in MAP form? use Tokyo 23 wards

```{r}
df_target_stations <-
  stations %>%
  # 観測装置の種類が「有線ロボット気象計」(いわゆるアメダス) であるものに制限
  filter(station_type %in% c("四")) %>%
  filter(block_no != "0092") %>%
  group_by(pref_code, area) %>%
  sample_n(1) %>%
  ungroup() %>%
  select(pref_code, area, station_name, block_no)



df_targets <-
  purrr::map2_dfr(
    .x = df_target_stations$block_no %>%
      set_names(),
    .y = df_target_stations$station_name,
    ~ jma_collect(item = "hourly",
                  block_no = .x,
                  year = 2018,
                  month = 7,
                  day = 31) %>% 
      select(date, time, starts_with("temperature")) %>% 
      #jmastats::parse_unit() %>% 
      mutate(station = .y),
    .id = "block_no")
```


# tile map of TOKYO avg. summer temperature (June-Sept) from Toyo Keizai: https://toyokeizai.net/sp/visual/tko/temperature/

```{r tile map tokyo summer}
library(jsonlite)
library(lubridate)

tokyo_his_temp <- jsonlite::read_json("data/temperature.json", simplifyVector = TRUE)

tokyo_weather_df <- tokyo_his_temp %>% 
  set_names(nm = 1876:2018) %>% 
  map(~as.data.frame(.) %>% 
        modify_if(., is.factor, as.character) %>% 
        modify_if(., is.character, as.numeric)) %>% 
  map2_df(., names(.), ~ mutate(., ID = .y)) %>% 
  rename(avg_temp = ".",
         year = ID)

# separate 2018 as data only up to 7/17
tokyo_weather_df_2018 <- tokyo_weather_df %>% 
  filter(year == 2018) %>% 
  mutate(
    date = seq.Date(from = as.Date("2018-06-01"), 
                    by = "day",
                    length = 47),
    date = format(date, "%m/%d")
  ) 
  
# rest of the years, then combine back
tokyo_weather_df <- tokyo_weather_df %>% 
  filter(year != 2018) %>% 
  group_by(year) %>% 
  mutate(
    date = seq.Date(from = as.Date("1876-06-01"), 
                    by = "day",
                    length = 122),
    date = format(date, "%m/%d")
  ) %>% 
  ungroup() %>% 
  full_join(tokyo_weather_df_2018) %>% 
  mutate(year = as.numeric(year))

glimpse(tokyo_weather_df)

```



```{r}
scale_fill_jma_absolute(
    type = "temperature", 
    guide = "colourbar",
    na.value = "grey50")

dichromat_pal("DarkRedtoBlue.12")(12)
dichromat_pal("DarkRedtoBlue.12")(12)[4:12]

cols <- c("#1a9641", "#a6d96a", "#ffffbf", "#fdae61", "#d7191c")

jmastats:::jma_pal(palette = "relative", .attribute = FALSE)[5:1]

```


```{r plot tokyo summer, fig.height=8, fig.width=10}
library(jmastats)
library(extrafont)
library(scales)
# loadfonts()

# colorbrewer2.org: diverging 8-class palette
cols <- rev(c('#d53e4f','#f46d43','#fdae61','#fee08b','#e6f598','#abdda4','#66c2a5','#3288bd'))

labels <- c("10", "12", "14", "16", "18", "20", "22", "24", "26", "28", "30", "32")

breaks <- c(seq(10, 32, by = 2))

tokyo_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile() +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  scale_y_reverse(limits = c(2017, 1876), expand = c(0, 0),
                  breaks = c(1876, seq(1880, 2015, by = 10), 2017)) +
  scale_x_discrete(breaks = c("06/01", "07/01", "08/01", "09/01", "09/30"),
                     labels = c("June 1st", "July 1st", "Aug. 1st", 
                                "Sept. 1st", "Sept. 30th")) +
  labs(title = "Summers in Tokyo are Getting Longer and Hotter (1876-2017)",
       subtitle = glue::glue("
          One Row = One Year, From June 1st to September 30th
          Average Temperature (Celsius)
          "),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed", size = 12),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(3, "cm"),
        plot.margin=unit(c(1,1,1.5,1.2),"cm"))

ggsave("tokyo_summer_temp_eng.png", plot = last_plot())
```



```{r LOG avg temp}
tokyo_log_weather_df <- tokyo_weather_df %>% 
  mutate(avg_temp = log10(avg_temp))


tokyo_log_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) + 
  geom_tile() + 
  scale_fill_jma_absolute() +
  scale_y_reverse(limits = c(2020, 1875), expand = c(0, 0))
```



```{r tile map JP version, fig.height=8, fig.width=10}
tokyo_weather_df %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile() +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("平均気温 " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  labs(title = "東京の夏は「暑く・長く」なっている (1876年～2017年)",
       subtitle = "6月1日～9月30日",
       caption = "データ：気象庁") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed", size = 12),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(3, "cm"))

ggsave("tokyo_summer_temp_jp.png", plot = last_plot(), width = 10, height = 8)
```



- caveat: tokyo prefecutreis very wide: from tokyo bay coastline all the way to mountainous Hachioji area
- not noted whether looking at tokyo weather from just the special 23 wards or the prefecture in general?
- figure out how to add dates grouped by year 
- >>> annoying is that 2018 only has 47 days recorded (as not september yet)...
- just filter out 2018 and set that individually??
- use ggiraph for interactivity?

# ggiraph:


```{r ggiraph data prep}
library(glue)

tokyo_weather_df_ggiraph <- tokyo_weather_df %>% 
  mutate(year = as.character(year),
         date = date %>% str_replace_all("/", "-")) %>% 
  unite(full_date, year, date, sep = "-", remove = FALSE) %>% 
  mutate(full_date = as.Date(full_date) %>% 
           format(., format = "%B %d, %Y"),
         ) %>% 
  glimpse()

tokyo_weather_df_ggiraph <- tokyo_weather_df_ggiraph %>% 
  filter(!year == 2018) %>% 
  mutate(tooltip = glue("
                        {full_date}: {avg_temp}{intToUtf8(176)}C"),
         year = as.numeric(year)) %>% glimpse()

tokyo_weather_df_ggiraph <- tokyo_weather_df_ggiraph %>% 
  filter(!year == 2018) %>% 
  mutate(tooltip = paste(full_date, ": ", avg_temp, intToUtf8(176), "C"),
         year = as.numeric(year)) %>% glimpse()

```

```{r ggiraph, fig.height=8, fig.width=10}
library(ggiraph)

tokyo_weather_ggiraph <- tokyo_weather_df_ggiraph %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile_interactive(aes(x = date, y = year, 
                            fill = avg_temp, 
                            tooltip = tokyo_weather_df_ggiraph$tooltip, 
                            data_id = tokyo_weather_df_ggiraph$tooltip)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df_ggiraph$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                label.position = "bottom",
                                nrow = 1)) +
  labs(title = "Average Temperature in Tokyo during the Summer (1876-2017)",
       subtitle = glue::glue("
          From June 1st to September 30th
          One Row = One Year"),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(1.5, "cm")) +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0))

ggiraph(code = print(tokyo_weather_ggiraph))

```







```{r}

tkw <- tokyo_weather_df_ggiraph %>% 
  ggplot(aes(x = date, y = year, fill = avg_temp)) +
  geom_tile_interactive(aes(x = date, y = year, 
                            fill = avg_temp, 
                            tooltip = tokyo_weather_df_ggiraph$tooltip, 
                            data_id = tokyo_weather_df_ggiraph$tooltip)) +
  scale_fill_gradientn(
    colours = cols,
    labels = labels,
    breaks = breaks,
    limits = c(11, max(tokyo_weather_df_ggiraph$avg_temp))) +
  guides(fill = guide_colorbar(title = expression("Temperature " ( degree~C)),
                                reverse = FALSE,
                                title.position = "left",
                                nrow = 1)) +
  labs(title = "Average Temperature in Tokyo during the Summer (1872-2017)",
       subtitle = glue::glue("
          From June 1st to September 30th
          One Row = One Year"),
       caption = "Data from Toyo Keizai News via Japan Meteorological Agency") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(2, "cm")) +
  scale_y_reverse(limits = c(2018, 1876), expand = c(0, 0))


ggiraph(code = print(tkw), dep_dir = "C:/Users/Ryo Nakagawara/Documents/R_materials/japan_weather_plots/output")

```


## cartograms



```{r}
ja_weather_df_fin %>% 
  filter(day == "dayone", type == "avg") %>% 
  st_transform(crs = "+init=epsg:3395") -> carto_base

pref_pop_hist %>% 
  filter(!prefectures == "Japan") %>% 
  mutate(code = as.numeric(code)) -> pref_pop_hist


pop_df <- ja_weather_df_fin %>% 
  mutate(jis_code = as.numeric(jis_code)) %>% 
  left_join(pref_pop_hist, c("jis_code" = "code")) %>% glimpse()


pop_df_base <- pop_df %>% 
  filter(day == "dayone", type == "avg", year == 2010) %>% 
  st_transform(crs = "+init=epsg:3395")

```



```{r}
library(tmap)


carto_df <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_dorling("temperature", itermax = 500)

tm_shape(ja_weather_df_fin) + 
  tm_borders() +
  tm_shape(carto_df) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

carto_df <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_dorling("population", itermax = 500)

tm_shape(carto_df) +
  tm_polygons("population", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

```


```{r}
#
carto_nca <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_ncont("temperature")

tm_shape(ja_weather_df_fin) + 
  tm_borders() +
  tm_shape(carto_nca) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)


carto_nca <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_ncont("population")

tm_shape(pop_df_base) + 
  tm_borders() +
  tm_shape(carto_nca) +
  tm_polygons("population", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)


```


```{r}
#

cart_cac <- carto_base %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_cont("temperature", itermax = 10)

tm_shape(cart_cac) +
  tm_polygons("temperature", style = "jenks", size = 0.5) +
  tm_layout(frame = FALSE)

carto_df <- pop_df_base %>% 
  st_transform(crs = "+init=epsg:3395") %>% 
  st_cast("MULTIPOLYGON") %>% 
  cartogram_cont("population")

tm_shape(carto_df) +
  tm_polygons("population", style = "pretty") +
  tm_layout(frame = FALSE)

```





# climate stripes from Ed Hawkins

- http://www.climate-lab-book.ac.uk/2018/warming-stripes/
Data from yearly measurement table (Japan Meteorological Agency):
- http://www.data.jma.go.jp/obd/stats/etrn/view/annually_s.php?prec_no=44&block_no=47662

```{r scrape JMA annuals}
url <- "http://www.data.jma.go.jp/obd/stats/etrn/view/annually_s.php?prec_no=44&block_no=47662"

session_jma <- url %>% 
  read_html() %>% 
  html_nodes("#tablefix1") %>% 
  .[[1]] %>% 
  html_table(fill = TRUE, header = FALSE)

# #tablefix1 > tbody:nth-child(1)


glimpse(session_jma)

tokyo_year_avg_temp <- session_jma %>% 
  select(year = X1, avg_temp = X8, avg_high = X9, avg_low = X10, 
         high_temp = X11, low_temp = X12) %>% 
  slice(-c(1, 2, 3)) %>% 
  mutate(avg_temp = avg_temp %>% str_remove("\\]") %>% as.numeric(),
         avg_high = avg_high %>% str_remove("\\]") %>% as.numeric(),
         avg_low = avg_low %>% str_remove("\\]") %>% as.numeric(),
         high_temp = high_temp %>% str_remove("\\]") %>% as.numeric(),
         low_temp = low_temp %>% str_remove("\\]") %>% as.numeric(),
         year = as_factor(year))

```

# bar code chart

```{r fig.height=6, fig.width=8}
# 10 Class Divergent Rd-Bu: http://colorbrewer2.org/#type=diverging&scheme=RdBu&n=10
temp_cols <- rev(c('#67001f','#b2182b','#d6604d','#f4a582','#fddbc7',
               '#d1e5f0','#92c5de','#4393c3','#2166ac','#053061'))

# filter out 1875 and 2018 due to uncertainties in the measurements

tokyo_year_avg_temp %>% 
  filter(!year %in% c(1875, 2018)) %>% 
  ggplot(aes(x = year, fill = avg_temp)) +
  geom_bar(position = "fill", width = 1) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_gradientn(colors = temp_cols, guide = FALSE) +
  theme_void() +
  theme(legend.position = "bottom")

ggsave(filename = "../output/tokyo_yearly_avg_temp.png", height = 6, width = 8)

range(tokyo_year_avg_temp$avg_temp) # 12.9 - 17.3
```

With titles + labels:

```{r fig.height = 6, fig.width=8}
tokyo_year_avg_temp %>% 
  filter(!year %in% c(1875, 2018)) %>% 
  ggplot(aes(x = year, fill = avg_temp)) +
  geom_bar(position = "fill", width = 1) +
  scale_y_continuous(expand = c(0, 0.01)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_gradientn(colors = temp_cols, "Average Temperature (Celsius)") +
  labs(title = "Tokyo: Annual Average Temperature (1876-2017)",
       subtitle = "One Stripe = One Year, Left: 1876, Right: 2017") +
  theme_void() +
  theme(text = element_text(family = "Roboto Condensed"),
        legend.position = "bottom",
        legend.title = element_text())

ggsave(filename = "../output/tokyo_yearly_avg_temp_LABS.png", height = 6, width = 8)
```



BAD:

```{r}
tokyo_year_avg_temp %>% 
  filter(!year %in% c(1875, 2018)) %>% 
  ggplot(aes(x = year, y = avg_temp, group = 1)) +
  geom_path() +
  geom_segment(aes(y = avg_high, yend = avg_low, x = year, xend = year)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 25)) + # NO!
  geom_point(aes(y = avg_high, x = year), color = "red") +
  geom_point(aes(y = avg_low, x = year), color = "blue") +
  geom_smooth() +
  scale_x_discrete(breaks = pretty_breaks(10)) +
  theme_minimal()
```

refer to: 
- https://callingbullshit.org/tools/tools_misleading_axes.html
- https://tamino.wordpress.com/2018/08/08/usa-temperature-can-i-sucker-you/

```{r}
tokyo_year_avg_temp %>% 
  filter(!year %in% c(1875, 2018)) %>% 
  ggplot(aes(x = year, y = avg_temp, group = 1)) +
  geom_path() +
  scale_y_continuous(expand = c(0, 0)) + 
  geom_smooth() +
  scale_x_discrete(breaks = pretty_breaks(10)) +
  theme_minimal()
```







# transition reveal: temperatures across time


```{r transition_reveal}
library(jmastats)
library(tidyr)

jmastats::stations %>% filter(station_type == "四") -> jma_stations

birthdayweather <- jma_collect(item = "hourly", block_no = "0370", 
                               year = 2017, month = 6, day = 28)

june_weather <- jma_collect(item = "daily", block_no = "0370", 
                               year = 2017, month = 6)

july_weather <- jma_collect(item = "daily", block_no = "0370", 
                               year = 2017, month = 7)

aug_weather <- jma_collect(item = "daily", block_no = "0370", 
                               year = 2017, month = 8)

list_we <- list(june_weather, july_weather, aug_weather)


sum_we <- list_we %>% 
  reduce(rbind)

sum_we_fin <- sum_we %>% 
  mutate(date = as_date(date) %>% ymd()) %>% 
  rename(avg_temp = `temperature_average(℃)`) %>% 
  separate(date, into = c("year", "month", "day"), sep = "-") %>% 
  mutate(month = as.numeric(month),
         day = as.numeric(day))

library(gganimate)

ggplot(sum_we_fin, aes(day, avg_temp, group = month)) +
  geom_line() +
  geom_segment(aes(xend = 31, yend = avg_temp)) +
  geom_point() +
  geom_text(aes(x = 31.1, label = month)) +
  transition_reveal(month, day) +
  ease_aes("linear")


```